\thetitle

### 2013-04-15 tfpie/tfpie.tex
Small fix to OO tests.
Fix bug in world program.

(check-expect (sum (new leaf% 7)) 7)
(check-expect 
  (sum (new node%
         (new leaf% 1)
         5 
         (new node% (new leaf% 0) 
                    10
                    (new leaf% 0))))
  16)
\end{verbatim}
\end{minipage}
\caption{Binary tree sum in Beginning Student and in our language}
\end{figure}

@@

  ;; to-draw : -> Image
  (define (on-tick) 
    (circle (this . n) "solid" "red"))

>>>>

(check-expect ((new leaf% 7) . sum) 7)
(check-expect 
  ((new node%
        (new leaf% 1)
        5 
        (new node% (new leaf% 0) 
                   10
                   (new leaf% 0))))
    . sum)
  16)
\end{verbatim}
\end{minipage}
\caption{Binary tree sum in Beginning Student and in our language}
\end{figure}

@@

  ;; to-draw : -> Image
  (define (to-draw) 
    (circle (this . n) "solid" "red"))
